---
title: "Spotify_data"
output: html_document
date: "2023-10-25"
runtime: shiny
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset

The dataset used:
<https://www.kaggle.com/datasets/nelgiriyewithana/top-spotify-songs-2023>

## Key Features

1.  track_name: Name of the song

2.  artist(s)*name: Name of the artist(s) of the song artist_count:
    Number of artists contributing to the song*

3.  *released_year: Year when the song was released*

4.  *released_month: Month when the song was released*

5.   *released_day: Day of the month when the song was released*

6.   *in_spotify_playlists: Number of Spotify playlists the song is
    included in*

7.  *in_spotify_charts: Presence and rank of the song on Spotify charts*

8.  *streams: Total number of streams on Spotify*

9.  *in_apple_playlists: Number of Apple Music playlists the song is
    included in*

10. *in_apple_charts: Presence and rank of the song on Apple Music
    charts in_deezer_playlists: Number of Deezer playlists the song is
    included in*

11. *in_deezer_charts: Presence and rank of the song on Deezer charts*

12. *in_shazam_charts: Presence and rank of the song on Shazam charts*

13. *bpm: Beats per minute, a measure of song tempo*

14. *key: Key of the song*

15. *mode: Mode of the song (major or minor)*

16. *danceability*%: Percentage indicating how suitable the song is for
    dancing

17. valence\_%: Positivity of the song's musical content

18. energy\_%: Perceived energy level of the song

19. acousticness\_%: Amount of acoustic sound in the song

20. instrumentalness\_%: Amount of instrumental content in the song

21. liveness\_%: Presence of live performance elements

22. speechiness\_%: Amount of spoken words in the song

## File:

```{r}
Spotify=read.csv2("C:/Users/liivi/Documents/Spotify/spotify-2023.csv",header = 1)
```


